Fast and optimal centroiding of faint stars

### 2014-12-12 ms/figure.tex
Update figure.tex

In this paper, we propose to find the centroid of stars by smoothing the image
of stars by a Gaussian kernel, and fitting a second order polynomial to
the $3\times$3 pixels around the brightest pixel of smoothed image.
We compare the accuracy of this method with, the naive 3\times$3 second-order 
polynomial method, the 3$\times$3 quartic approximation
method used in SDSS photometric pipeline, and fitting a PSF model to the 
star.

@@

\subsection{3$\times$3 modified polynomial method}
Now, we modify the simple polynomial method explained above,
by smoothing the image of the star with a Gaussian kernel
\beq
k(x) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
\eeq
Throughout this study, we keep the width of the Gaussian kernel $w$ constant.
Then we apply the same polynomial method to the 3$\times$3 patch around the brightest
pixel of the smoothed image. The important difference between the previous
approach and the modified method is that, there are non-zero covariances
among the uncertainties of the brightness of different pixels of the
smoothed image. That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
It can be shown that after smoothing, elements of the covariance matrix are given by
\begin{eqnarray}
\mathbf{C}_{ij} &=& \frac{\sigma^{2}}{4\pi w^{2}} \exp(-\frac{r_{ij}^{2}}{4\pi w^{2}}),\\
r_{ij}^{2} &=& (x_{i} - x_{j})^{2} + (y_{i} - y_{j})^{2},
\label{nondiagonal}
\end{eqnarray}
where $w$ is width of the kernel, $\sigma$ is the per-pixel uncertainty, and $x_{i}$
, $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel
respectively. In the presence of the non-diagonal covariance matrix
$\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
\beq
\mathbf{X} = [\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{A}]^{-1}[\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{Z}].
\label{linearfit2}
\eeq
Therefore, for a given star and a smoothing kernel,
the outcome of equation (\ref{linearfit2}) can be
plugged into equation (\ref{center}) to find the centroid estimate
of the star.
\subsection{3$\times$3 quartic approximation method}
Consider any row or column of the 3$\times$3 patch around
the brightest pixel of the smooth image and let us denote
the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
The fundamental assumption behind the technique is that these
brightness values can be approximated
by the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$
evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid
of the three pixels. Knowing the value of $P$ at $\{-1,0,1\}$,
expanding $P(x)$ up to fourth order in $x$ leads to
\beq
x = \frac{s}{t}(1+k\frac{t}{4Q}(1-(s/t)^{2})),
\eeq
where k = 1.33, and

@@

We perform two sets of simulations. In the first set, we choose four values of
2, 2.8, 4, and 5.6 pixels for $\gamma$. For each $\gamma$, we generate 100,000 
17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, Gaussian
is noise added to each postage-stamp such that the stars are uniformly distributed
in log-SNR between SNR = 5 to SNR = 150.

@@

After finding the centroiding error for each method, we
compute the RMSE in bins of SNR.
Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}].
As we expected, for all methods, median squared error becomes larger for fainter stars,
and for stars with larger $\gamma$. As it can be seen in figure [\ref{1}],
centroid estimate obtained from the polynomial method does not saturate
the CRLB unless at smaller values of SNR.

The modified polynomial centroiding however, is able to deliver
median squared error arbitrarily close to the CRLB in all ranges
of SNR. At $\gamma = 2$ the modified centroiding estimate does not
saturates the CRLB, but as $\gamma$ gets larger,
centroid estimates of this techniques saturate and eventually,
get lower than the CRLB. The median error from the SDSS method
shows similar behaviour to that of modified polynomial method.
See figures [\ref{2}], [\ref{3}].
And finally, the centroid estimates from the exact fitting the exact PSF
model give rise to a median error that is always below the CRLB [\ref{4}].

\subsection{Experiment 2}

Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{5}], [\ref{6}], [\ref{7}], and [\ref{8}]. 
By decreasing noise level of the background sky, $\Delta x$ becomes smaller at all ranges of $\gamma$.

The polynomial method fails to saturate the CRLB except in simulations with SNR of 5. The modified polynomial method, and the SDSS method result in  median squared error always lower than CRLB, except in simulated stars with small $\gamma$. As we expect, the median error from fitting the exact PSF model always saturates the CRLB.

\subsection{Elliptical PSF}

In the last experiment, we compare the performances of the modified polynomial method, and SDSS method, with fitting the exact PSF model to the elliptical Moffat profiles, and also with fitting a circular PSF model.

The median error from the modified polynomial and SDSS methods are very close to the CRLB. But only by fitting an approximate (circular) PSF profile, or eventually by fitting an exact PSF model, one can saturate the CRLB. However, it is important to note that centroiding errors of all four methods are extremely close to each other.

@@

In this work, we proposed a method for centroiding stars based on fitting a low order polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. Employing this technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys. The advantage of this method becomes more pronounced in PSF estimation in which we need to know the centroid of stars accurately, but at the same time, with fewer number of algebraic operations.

This method can roughly be thousand times faster than centroiding through model fitting, and requires fewer operations than the method implemented in SDSS photo pipeline. More importantly, it requires no prior knowledge about the shape of the PSF.

Comparison of this technique with the centroiding method based on a fourth-order approximation implemented in SDSS photo pipeline suggests that in wide ranges of size and noise level of the background sky, the error arising from this method is close to the theoretically set CRLB, and comparable to the error obtained from SDSS method.

Although having a reasonable PSF model should always deliver better centroid estimates, one can achieve sensibly accurate results by employing this simple 3$\times$3 method without making any assumption about the PSF model.

@@

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_poly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{1}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_spoly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{2}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_sdss.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the SDSS method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{3}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_fitting.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{4}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_poly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_spoly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_sdss.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the SDSS method and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_fitting.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 50 (upper right), 100 (lower left), and 150 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{8}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from: the SDSS method (upper left), the modified polynomial method (upper right), fitting circular PSF model (lower left), and  fitting the exact PSF model (lower right) and SNR of stars with major axis of 2.8 pixels and ellipticity of 0.2. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{9}
\end{figure}

>>>>

In this paper, we propose to find the centroid of stars by smoothing the image
of stars by a Gaussian kernel, and fitting a second order polynomial to
the $3\times$3 pixels around the brightest pixel of smoothed image.
We compare the accuracy of this method with, the naive 3$\times$3 second-order 
polynomial method, the 3$\times$3 quartic approximation
method used in SDSS photometric pipeline, and fitting a PSF model to the 
star.

@@

\subsection{3$\times$3 modified polynomial method}
Now, we modify the simple polynomial method explained above,
by smoothing the image of the star with a Gaussian kernel
\beq
k(\mathbf{x}) = \frac{1}{2\pi w^2}\exp(-\mathbf{x}^{2}/2w^{2}).
\eeq
Throughout this study, we keep the width of the Gaussian kernel $w$ constant.
Then we apply the same polynomial method to the 3$\times$3 patch around the brightest
pixel of the smoothed image. The important difference between the previous
approach and the modified method is that, there are non-zero covariances
among the uncertainties of the brightness of different pixels of the
smoothed image. That is, the covariance matrix $\mathbf{C}$ is non-diagonal.
It can be shown that after smoothing, elements of the covariance matrix are given by
\begin{eqnarray}
\mathbf{C}_{ij} &=& \frac{\sigma^{2}}{4\pi w^{2}} \exp(-\frac{r_{ij}^{2}}{4\pi w^{2}}),\\
r_{ij}^{2} &=& (x_{i} - x_{j})^{2} + (y_{i} - y_{j})^{2},
\label{nondiagonal}
\end{eqnarray}
where $w$ is width of the kernel, $\sigma$ is the per-pixel uncertainty, and $x_{i}$
, $y_{i}$ are the $x$, and $y$ coordinates of the $i$-th pixel
respectively. In the presence of the non-diagonal covariance matrix
$\mathbf{C}$, equation (\ref{linearfit}) needs to be modified in the following way
\beq
\mathbf{X} = [\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{A}]^{-1}[\mathbf{A}^{T}\mathbf{C}^{-1}\mathbf{Z}].
\label{linearfit2}
\eeq
Therefore, for a given star and a smoothing kernel,
the outcome of equation (\ref{linearfit2}) can be
plugged into equation (\ref{center}) to find the centroid estimate
of the star.
\subsection{3$\times$3 quartic approximation method}
Consider any row or column of the 3$\times$3 patch around
the brightest pixel of the smooth image and let us denote
the brightness of these three pixels by $\{I_{-},I_{0},I_{+}\}$.
The fundamental assumption behind the technique is that these
brightness values can be approximated
by the function $P(x) = Q\exp((x-x_{c})^{2}/2\beta^{2})$
evaluated at $x=-1,0,+1$; with $x_{c}$ being the position of centroid
of the three pixels. Knowing the value of $P$ at $\{-1,0,1\}$,
expanding $P(x)$ up to fourth order in $x$ leads to
\beq
x = \frac{s}{t}(1+k\frac{t}{4Q}(1-(s/t)^{2})),
\eeq
where k = 1.33, and

@@

We perform two sets of simulations. In the first set, we choose four values of
2, 2.8, 4, and 5.6 pixels for $\gamma$. For each $\gamma$, we generate 100,000 
17 $\times$ 17 postage-stamps of Moffat profiles with centroids randomly drawn
within the central pixel of the 17 $\times$ 17 postage-stamps. Moreover, Gaussian
is noise added to each postage-stamp such that the stars are uniformly distributed
in log-SNR between SNR = 5 to SNR = 100.

@@

In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of SNR in order to compare it to the CRLB. 
Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}], [\ref{5}]. All methods deliver results with RMSE larger for fainter stars.
In case of 3$\times$3 polynomial centroiding [\ref{1}], RMSE becomes very large as we move towards the fainter stars in our simulation. Moreover, we observe a kink in the plot of RMSE against SNR. For stars with larger $\gamma$, this kink moves toward higher values of SNR. As it can be seen in figure [\ref{1}], centroid estimate from the polynomial method do not even get close to saturating the CRLB. By increasing $\gamma$, RMSE moves further away from the CRLB.

However, RMSE from the modified centroiding method [\ref{2}], and RMSE from the quartic approximation [\ref{3}] method are very close to the CRLB. As we increase $\gamma$ from 2 pixels to 2.8 pixels, RMSE gets closer to the CRLB. This implies that as stars get undersampled, the performance of these two models get slightly worse. But if we increase $\gamma$ to 4 and 5.6 pixels, RMSE gets farther from the CRLB. This is quite predictable since these two models only use the information contained in a 3$\times$ 3 patch. It is also important to note that the rate at which the RMSE from these two method drops eventually becomes smaller than the constant rate at which the CRLB decreases with increaing SNR.

As we expected, the RMSE from centroiding by fitting the exact PSF model [\ref{4}] lies on the CRLB. Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB. As it can be seen in figure [\ref{5}], even the centroid estimates found by fitting a wrong PSF model (Gaussian PSF) to the simulated stars saturate the CRLB.

\subsection{Experiment 2}
In this experiment, after finding the centroiding error for each method, we compute the RMSE in bins of $\gamma$ in order to compare it to the CRLB. 
Behavior of error as a function of $\gamma$ for different values of SNR, is shown in figures [\ref{6}], [\ref{7}], and [\ref{8}], [\ref{9}], and [\ref{10}].

The centroid estimates obtained from the 3$\times$3 polynomial method [\ref{6}] result in RMSE much larger than the CRLB in all ranges of FWHM and for all four values of SNR in this experiment. In the case of extremely faint stars (SNR = 5), the polynomial method is not able to deliver any reliable estimate, and completely fails.

The 3$\times$3 modified polynomial method [\ref{7}], and the 3$\times$3 quartic approximation [\ref{8}] result in RMSE very close to the CRLB. For al four values of SNR, as we increase $\gamma$ from 2 pixels to 3 pixels, RMSE gets slightly closer to the CRLB since these two models start to work slightly worse as we decrease $\gamma$ and move towards undersampled stars. After approximately 3 pixels, increasing $\gamma$ deviate RMSE of these methods from the CRLB. This is inherent characteristic of all 
3$\times$3 methos. Furthermore, increasing SNR from 5 to 40 makes the RMSE (as a function of $\gamma$) closer to the CRLB.

Again The RMSE from centroiding by fitting the exact PSF model as a function of FWHM perfectly lies on the CRLB [\ref{9}]. Thus, centroid estimates from fitting the exact PSF model always saturate the CRLB. Once again, we observe that the centroid estimates found by fitting a Gaussian PSF to the simulated stars also saturate the CRLB in all ranges of $\gamma$ [\ref{10}].

@@

In this work, we proposed a method for centroiding stars based on fitting a low order polynomial to a 3$\times$3 patch of star images smoothed by a Gaussian kernel. 
Furthermore, we compared the performance of this method with the naive 3$\times$3 polynomial centroiding, 3$\times$3 quartic approximation, and PSF fitting.
In order to make this comparison, we performed some tests on a large number of simulated data, and investigated to see if these estimators can saturate the Cramer-Rao lower bound, or how close to they get to saturating the bound.

Our results suggest that in all ranges of FWHM and SNR, the PSF fitting method returns centroid estimates that saturate the CRLB. We found that the estimates found by 3$\times$3 polynomial method are far away from saturating the CRLB. On the other hand, the RMSE of centroid estimates of our proposed 3$\times$3 modified polynomial method, and that of the 3$\times$3 quartic approximation, are much closer to the CRLB. The performance of these two methods however, is limited by two important factors: \emph{(i)} signal-to-noise ratio, and \emph{(ii)} size of the stars.

These two techniques only take advantage of the information contained in a 3$\times$3 patch around the brighest pixel of the smoothed image. Thus, when we apply 
these methods to find the centroid of stars with larger FWHM, a certain amount of information (encoded in the Cramer-Rao lower bound) is lost, and therefore, the RMSE of these methods deviates from the CRLB. This deviation gets even larger at lower signal-to-noise ratios. Besides, the performance of these methods slightly degrades in the case of undersampled stars. Presence of noise is another limitting factor. Although these methods are able to get close to saturating the CRLB in a wide range of signal-to-noise ratios, they are not as reliable in the extremely faint stars (SNR less than 10). This is mostly due to the fact that presence of noise could move the true brightest pixel of image.

In this investigation we showed that PSF fitting is always better at centroiding stars. In practice however, we do no know the the exact PSF. Besides finding the centroid by PSF fitting is computationally expensive whereas by employing tht 3$\times$3 modified polynomial technique into large scale astronomical surveys can considerably reduce the computational cost of initial astrometry of these surveys. The advantage of this method becomes more pronounced in PSF estimation in which we need to know the centroid of stars accurately, but at the same time, with fewer number of algebraic operations. This method can roughly be thousand times faster than centroiding by model fitting, and requires fewer operations than the 3$\times$3 quartic approximation mehod.

Having a reasonable PSF model should always deliver better centroid estimates, but over a certain range of low signal-to-noise ratios, one can achieve sensibly accurate results by employing this simple 3$\times$3 method without making any assumption about the PSF model.

@@

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_poly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{1}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_spoly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{2}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_sdss.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic aproximation method and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{3}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_psf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{4}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{snr_wrongpsf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model to the stars and the signal-to-noise ratio of stars, with FWHM of : 2 (upper left), 2.8 (upper right), 4 (lower left), and 5.6 (lower right) pixels. In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{5}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_poly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{6}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_spoly.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 modified polynomial method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{7}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_sdss.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from the 3$\times$3 quartic approximation method and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{8}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_psf.png}
\endminipage
\caption{Scatter plots showing the relation between error in centroid measurement from fitting the exact PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{9}
\end{figure}

\begin{figure}[!htb]
\minipage{.8\textwidth}
  \includegraphics[width=\linewidth]{fwhm_wrongpsf.png}
\endminipage
\captionScatter plots showing the relation between error in centroid measurement from fitting a Gaussian PSF model and FWHM of stars, with SNR  of : 5 (upper left), 10 (upper right), 20 (lower left), and 40 (lower right). In each scatter plot, the blue line represents the running median of data points, and the green line represents CRLB.}\label{10}
\end{figure}
